Data Appendix to \"The impact of weather events on schooling outcomes\

### 2020-04-26 data_appendix_all_years.Rmd
commit spacing
another subset of regressions

```{r import household data 2005}
data_2005 <- read_dta("Raw data/seminar_paper_data/2005_hhsurvey.dta") %>% 
  rename(hh_id = folio,
        assist = s3_08,  
        reason = s3_09, 
        members = nm_y,
        sex = s1_02,
        age = s1_03,
        relation = s1_05,
        literacy = s3_01,
        register = s3_04,
        school_level = s3_05a,
        grade = s3_05b,
        repeated = s3_07,
        income = y_perc1A,
        educ = aoesc,
        job = s4_16cod,
        tasks = s4_16b,
        pov_line = z,
        extr_pov = z_ext)

hh_2005 <- data_2005 %>% 
  select(hh_id, assist, reason, sex, age,
         relation, literacy, register, school_level, grade, repeated, depto, urb_rur, income, educ, job, tasks, pov_line, extr_pov) %>% 
  mutate(year = 2005,
         dept = case_when(depto == "1" ~ "Chuquisaca",
                          depto == "2" ~ "La Paz",
                          depto == "3" ~ "Cochabamba",
                          depto == "4" ~ "Oruro",
                          depto == "5" ~ "Potosi",
                          depto == "6" ~ "Tarija",
                          depto == "7" ~ "Santa Cruz",
                          depto == "8" ~ "Beni",
                          depto == "9" ~ "Pando"),
         reason = case_when(reason == 1 ~ 'vacation',
                            reason == 2 ~ 'money', 
                            reason == 3 ~ 'work', 
                            reason == 4 ~ 'sickness/accident/disability', 
                            reason == 5 ~ 'distance',
                            reason == 6 ~ 'finished', 
                            reason == 7 ~ 'age',
                            reason == 8 ~ 'not interested', 
                            reason == 9 ~ 'housework/childcare',
                            reason == 10 ~ 'other'))

@@

```{r import household data 2006}
data_2006 <- read_dta("Raw data/seminar_paper_data/2006_hhsurvey.dta")  %>% 
  rename(hh_id = Folio,
        assist = s4_08,  
        reason = S4_09, 
        members = mhogar,
        sex = s1_02,
        age = s1_03,
        relation = s1_05,
        literacy = s4_01,
        register = s4_04,
        school_level = s4_05a,
        grade = s4_05b,
        repeated = s4_07,
        income = yhogpcf,
        urb_rur = Urb_Rur,
        depto = ID01,
        educ = añoe,
        job = s5_17cod,
        tasks = s5_16b,
        pov_line = z,
        extr_pov = zext)

hh_2006 <- data_2006 %>% 
  select(hh_id, assist, reason, sex, age,
         relation, literacy, register, school_level, grade, repeated, depto, urb_rur, income, educ, job, tasks, pov_line, extr_pov) %>% 
  mutate(year = 2006,
         dept = case_when(depto == "1" ~ "Chuquisaca",
                          depto == "2" ~ "La Paz",
                          depto == "3" ~ "Cochabamba",
                          depto == "4" ~ "Oruro",
                          depto == "5" ~ "Potosi",
                          depto == "6" ~ "Tarija",
                          depto == "7" ~ "Santa Cruz",
                          depto == "8" ~ "Beni",
                          depto == "9" ~ "Pando"),
           reason = case_when(reason == 1 ~ 'vacation',
                            reason == 2 ~ 'money', 
                            reason == 3 ~ 'work', 
                            reason == 4 ~ 'sickness/accident/disability', 
                            reason == 5 ~ 'distance',
                            reason == 6 ~ 'finished', 
                            reason == 7 ~ 'age',
                            reason == 8 ~ 'not interested', 
                            reason == 9 ~ 'housework/childcare',
                            reason == 10 ~ 'other'))
```

@@

```{r import household data 2007}
data_2007 <- read_dta("Raw data/seminar_paper_data/2007_hhsurvey.dta")  %>% 
  rename(hh_id = folio,
        assist = s4_10,  
        reason = s4_11, 
        members = mhogar,
        sex = s1_03,
        age = s1_04,
        relation = s1_06,
        literacy = s4_01,
        register = s4_06,
        school_level = s4_07a,
        grade = s4_07b,
        repeated = s4_09,
        income = yhogpcf,
        voucher = s4_05,
        educ = a_oe,
        job = s5_16co,
        tasks = s5_16b,
        pov_line = z,
        extr_pov = zext)

hh_2007 <- data_2007 %>% 
  select(hh_id, assist, reason, sex, age,
         relation, literacy, register, school_level, grade, repeated, depto, urb_rur, income, educ, job, tasks, pov_line, extr_pov) %>% 
  mutate(year = 2007,
         dept = case_when(depto == "1" ~ "Chuquisaca",
                          depto == "2" ~ "La Paz",
                          depto == "3" ~ "Cochabamba",
                          depto == "4" ~ "Oruro",
                          depto == "5" ~ "Potosi",
                          depto == "6" ~ "Tarija",
                          depto == "7" ~ "Santa Cruz",
                          depto == "8" ~ "Beni",
                          depto == "9" ~ "Pando"),
           reason = case_when(reason == 1 ~ 'vacation',
                            reason == 2 ~ 'money', 
                            reason == 3 ~ 'work', 
                            reason == 4 ~ 'sickness/accident/disability', 
                            reason == 5 ~ 'distance',
                            reason == 6 ~ 'finished', 
                            reason == 7 ~ 'age',
                            reason == 8 ~ 'not interested', 
                            reason == 9 ~ 'housework/childcare',
                            reason == 10 ~ 'other'))
```

```{r import household data 2011}
data_2011 <- read_dta("Raw data/seminar_paper_data/2011_hhsurvey.dta")  %>% 
  rename(hh_id = folio,
        assist = s4_12,  
        reason = s4_13,
        sex = s1_03,
        age = s1_04,
        relation = s1_08,
        literacy = s4_01,
        register = s4_05,
        grade = s4_06b,
        repeated = s4_11a,
        income = yhogpc,
        school_level = s4_06a,
        urb_rur = area,
        breakfast = s4_07,
        voucher = s4_08,
        voucher_spent = s4_09,
        educ = e,
        job = cod_16a,
        tasks = s5_16b,
        pov_line = z,
        extr_pov = zext)

hh_2011 <- data_2011 %>% 
  select(hh_id, assist, reason, sex, age,
         relation, literacy, register, school_level, grade, repeated, depto, urb_rur, income, educ, job, tasks, pov_line, extr_pov) %>% 
  mutate(year = 2011,
         dept = case_when(depto == "1" ~ "Chuquisaca",
                          depto == "2" ~ "La Paz",
                          depto == "3" ~ "Cochabamba",
                          depto == "4" ~ "Oruro",
                          depto == "5" ~ "Potosi",
                          depto == "6" ~ "Tarija",
                          depto == "7" ~ "Santa Cruz",
                          depto == "8" ~ "Beni",
                          depto == "9" ~ "Pando"),
           reason = case_when(reason == 1 ~ 'vacation',
                            reason == 2 ~ 'money', 
                            reason == 3 ~ 'work', 
                            reason == 4 ~ 'sickness/accident/disability', 
                            reason == 5 ~ 'distance',
                            reason == 6 ~ 'finished', 
                            reason == 7 ~ 'age',
                            reason == 8 ~ 'not interested', 
                            reason == 9 ~ 'housework/childcare',
                            reason == 10 ~ 'other'))
```

```{r household data 2012}
data_2012 <- read_dta("Raw data/seminar_paper_data/2012_hhsurvey.dta")  %>% 
  rename(hh_id = folio,
        assist = s4_12,  
        reason = s4_13,
        sex = s1_03,
        age = s1_04,
        relation = s1_08,
        literacy = s4_01,
        register = s4_04,
        grade = s4_05b,
        repeated = s4_11a,
        income = yhogpc,
        school_level = s4_05a,
        urb_rur = area,
        depto = departamento,
        breakfast = s4_07,
        voucher = s4_08,
        voucher_spent = s4_09,
        educ = e,
        job = cods5_16a,
        tasks = s5_16b,
        pov_line = z,
        extr_pov = zext)

hh_2012 <- data_2012 %>% 
  select(hh_id, assist, reason, sex, age,
         relation, literacy, register, school_level, grade, repeated, depto, urb_rur, income, educ, job, tasks, pov_line, extr_pov) %>% 
  mutate(year = 2012,
         dept = case_when(depto== "1" ~ "Chuquisaca",
                          depto == "2" ~ "La Paz",
                          depto == "3" ~ "Cochabamba",
                          depto == "4" ~ "Oruro",
                          depto == "5" ~ "Potosi",
                          depto == "6" ~ "Tarija",
                          depto == "7" ~ "Santa Cruz",
                          depto == "8" ~ "Beni",
                          depto == "9" ~ "Pando"),
           reason = case_when(reason == 1 ~ 'vacation',
                            reason == 2 ~ 'money', 
                            reason == 3 ~ 'work', 
                            reason == 4 ~ 'sickness/accident/disability', 
                            reason == 5 ~ 'distance',
                            reason == 6 ~ 'finished', 
                            reason == 7 ~ 'age',
                            reason == 8 ~ 'not interested', 
                            reason == 9 ~ 'housework/childcare',
                            reason == 10 ~ 'other'))
```

@@

``` {r merging datasets}
total_data<- all_years %>% 
  left_join(flood_summary) %>%
  left_join(drought_summary)

@@

hh_head <- subset(total_data, relation == 1, select = c("hh_id", "sex", "age", "literacy", "dept", "urb_rur", "income", "year", "educ", "job", "tasks", "pov_line", "extr_pov"))

@@

children <- subset(total_data, age < 18 & age > 4, select = c("hh_id", "age", "sex", "relation", "literacy", "dept", "urb_rur", "income", "assist", "reason", "register", "school_level", "grade", "repeated", "floods", "droughts", "year", "job", "tasks"))

@@

@@

```{r combining household head characteristics with children dataset}
hh_head_2 <- hh_head %>%
  select(sex, age, literacy, educ, job, tasks, pov_line, extr_pov, hh_id) %>%
  rename (female_hhhead = sex,
          hhhead_age = age,
          hhhead_literacy = literacy,
          hhhead_educ = educ,
          hhhead_job = job,
          hhhead_tasks = tasks)
total_heads_subset <- hh_head_2 %>% distinct()

@@

```{r regression variable specifications}
reg_data <- total_subset %>%
  mutate(ln_income = log(income),
         literate = literacy - 1,
         female = case_when(sex == 2 ~ 1,
                            sex == 1 ~ 0),
         no_assist = assist - 1,
         not_registered = register - 1,
         year_factor = as.factor(year))

@@

#model_simple <- lm(assist ~ floods + droughts + year, data = reg_data)
#summary(model_simple)
#model_assist <- lm(assist ~ floods + droughts + age + sex + income + hhhead_educ + female_hhhead + year, data = reg_data)
#summary(model_assist)
model_register <- lm(register ~ floods + droughts + age + sex + income + hhhead_educ + female_hhhead + year, data = reg_data)
summary(model_register)

@@

```{r generate regression table, echo = F, results = "asis"}
stargazer::stargazer(list(model_assist, model_register), 
               title = "Full sample regression results", 
               label = "fullResults",
               header = F,
               keep = c("floods", "droughts"))
```

@@

rural <- subset(reg_data, urb_rur == 2, select = c("hh_id", "id", "age", "sex", "literacy", "dept", "urb_rur", "income", "assist", "register", "floods", "droughts", "year", "job", "tasks", "num_children", "female_hhhead", "hhhead_literacy", "hhhead_educ", "year_factor"))

model_assist_r <- lm(assist ~ floods + droughts + age + sex + income + hhhead_educ + female_hhhead + urb_rur + year, data = reg_data)
summary(model_assist_r)
model_register_r <- lm(register ~ floods + droughts + age + sex + income + hhhead_educ + female_hhhead + urb_rur + year, data = reg_data)
summary(model_register_r)

@@

>>>>

```{r import household data 2005}
data_2005 <- read_dta("Raw data/seminar_paper_data/2005_hhsurvey.dta") %>% 
  rename(hh_id = folio,
        assist1 = s3_08,  
        reason = s3_09, 
        members = nm_y,
        sex = s1_02,
        age = s1_03,
        relation = s1_05,
        literacy1 = s3_01,
        register1 = s3_04,
        school_level = s3_05a,
        grade = s3_05b,
        repeated = s3_07,
        income = y_perc1A,
        educ = aoesc,
        job = s4_16cod,
        tasks = s4_16b,
        pov_line = z,
        extr_pov = z_ext)

hh_2005 <- data_2005 %>% 
  select(hh_id, assist1, reason, sex, age,
         relation, literacy1, register1, school_level, grade, repeated, depto, urb_rur, income, educ, job, tasks, pov_line, extr_pov) %>% 
  mutate(year = 2005,
         dept = case_when(depto == "1" ~ "Chuquisaca",
                          depto == "2" ~ "La Paz",
                          depto == "3" ~ "Cochabamba",
                          depto == "4" ~ "Oruro",
                          depto == "5" ~ "Potosi",
                          depto == "6" ~ "Tarija",
                          depto == "7" ~ "Santa Cruz",
                          depto == "8" ~ "Beni",
                          depto == "9" ~ "Pando"),
         reason = case_when(reason == 1 ~ 'vacation',
                            reason == 2 ~ 'money', 
                            reason == 3 ~ 'work', 
                            reason == 4 ~ 'sickness/accident/disability', 
                            reason == 5 ~ 'distance',
                            reason == 6 ~ 'finished', 
                            reason == 7 ~ 'age',
                            reason == 8 ~ 'not interested', 
                            reason == 9 ~ 'housework/childcare',
                            reason == 10 ~ 'other'),
          literacy = case_when(literacy1 == 1 ~ 1,
                              literacy1 == 2 ~ 0), 
         female = case_when(sex == 2 ~ 1,
                            sex == 1 ~ 0),
         rural = case_when(urb_rur == 1 ~ 0,
                           urb_rur == 2 ~ 1), 
         assist = case_when(assist1 == 1 ~ 1,
                            assist1 == 2 ~ 0),
         register = case_when(register1 == 1 ~ 1,
                              register1 == 2 ~ 0),
         primary = case_when(school_level == 17 ~ 1,
                             school_level != 17 ~ 0),
         secondary = case_when(school_level == 18 ~ 1,
                               school_level != 18 ~ 0))

@@

```{r import household data 2006}
data_2006 <- read_dta("Raw data/seminar_paper_data/2006_hhsurvey.dta")  %>% 
  rename(hh_id = Folio,
        assist1 = s4_08,  
        reason = S4_09, 
        members = mhogar,
        sex = s1_02,
        age = s1_03,
        relation = s1_05,
        literacy1 = s4_01,
        register1 = s4_04,
        school_level = s4_05a,
        grade = s4_05b,
        repeated = s4_07,
        income = yhogpcf,
        urb_rur = Urb_Rur,
        depto = ID01,
        educ = añoe,
        job = s5_17cod,
        tasks = s5_16b,
        pov_line = z,
        extr_pov = zext)

hh_2006 <- data_2006 %>% 
  select(hh_id, assist1, reason, sex, age,
         relation, literacy1, register1, school_level, grade, repeated, depto, urb_rur, income, educ, job, tasks, pov_line, extr_pov) %>% 
  mutate(year = 2006,
         dept = case_when(depto == "1" ~ "Chuquisaca",
                          depto == "2" ~ "La Paz",
                          depto == "3" ~ "Cochabamba",
                          depto == "4" ~ "Oruro",
                          depto == "5" ~ "Potosi",
                          depto == "6" ~ "Tarija",
                          depto == "7" ~ "Santa Cruz",
                          depto == "8" ~ "Beni",
                          depto == "9" ~ "Pando"),
           reason = case_when(reason == 1 ~ 'vacation',
                            reason == 2 ~ 'money', 
                            reason == 3 ~ 'work', 
                            reason == 4 ~ 'sickness/accident/disability', 
                            reason == 5 ~ 'distance',
                            reason == 6 ~ 'finished', 
                            reason == 7 ~ 'age',
                            reason == 8 ~ 'not interested', 
                            reason == 9 ~ 'housework/childcare',
                            reason == 10 ~ 'other'),
          literacy = case_when(literacy1 == 1 ~ 1,
                              literacy1 == 2 ~ 0), 
         female = case_when(sex == 2 ~ 1,
                            sex == 1 ~ 0),
         rural = case_when(urb_rur == 1 ~ 0,
                           urb_rur == 2 ~ 1), 
         assist = case_when(assist1 == 1 ~ 1,
                            assist1 == 2 ~ 0),
         register = case_when(register1 == 1 ~ 1,
                              register1 == 2 ~ 0),
         primary = case_when(school_level == 17 ~ 1,
                             school_level != 17 ~ 0),
         secondary = case_when(school_level == 18 ~ 1,
                               school_level != 18 ~ 0))
```

@@

```{r import household data 2007}
data_2007 <- read_dta("Raw data/seminar_paper_data/2007_hhsurvey.dta")  %>% 
  rename(hh_id = folio,
        assist1 = s4_10,  
        reason = s4_11, 
        members = mhogar,
        sex = s1_03,
        age = s1_04,
        relation = s1_06,
        literacy1 = s4_01,
        register1 = s4_06,
        school_level = s4_07a,
        grade = s4_07b,
        repeated = s4_09,
        income = yhogpcf,
        voucher = s4_05,
        educ = a_oe,
        job = s5_16co,
        tasks = s5_16b,
        pov_line = z,
        extr_pov = zext)

hh_2007 <- data_2007 %>% 
  select(hh_id, assist1, reason, sex, age,
         relation, literacy1, register1, school_level, grade, repeated, depto, urb_rur, income, educ, job, tasks, pov_line, extr_pov) %>% 
  mutate(year = 2007,
         dept = case_when(depto == "1" ~ "Chuquisaca",
                          depto == "2" ~ "La Paz",
                          depto == "3" ~ "Cochabamba",
                          depto == "4" ~ "Oruro",
                          depto == "5" ~ "Potosi",
                          depto == "6" ~ "Tarija",
                          depto == "7" ~ "Santa Cruz",
                          depto == "8" ~ "Beni",
                          depto == "9" ~ "Pando"),
           reason = case_when(reason == 1 ~ 'vacation',
                            reason == 2 ~ 'money', 
                            reason == 3 ~ 'work', 
                            reason == 4 ~ 'sickness/accident/disability', 
                            reason == 5 ~ 'distance',
                            reason == 6 ~ 'finished', 
                            reason == 7 ~ 'age',
                            reason == 8 ~ 'not interested', 
                            reason == 9 ~ 'housework/childcare',
                            reason == 10 ~ 'other'),
          literacy = case_when(literacy1 == 1 ~ 1,
                              literacy1 == 2 ~ 0), 
         female = case_when(sex == 2 ~ 1,
                            sex == 1 ~ 0),
         rural = case_when(urb_rur == 1 ~ 0,
                           urb_rur == 2 ~ 1), 
         assist = case_when(assist1 == 1 ~ 1,
                            assist1 == 2 ~ 0),
         register = case_when(register1 == 1 ~ 1,
                              register1 == 2 ~ 0),
         primary = case_when(school_level == 17 ~ 1,
                             school_level != 17 ~ 0),
         secondary = case_when(school_level == 18 ~ 1,
                               school_level != 18 ~ 0))
```

```{r import household data 2011}
data_2011 <- read_dta("Raw data/seminar_paper_data/2011_hhsurvey.dta")  %>% 
  rename(hh_id = folio,
        assist1 = s4_12,  
        reason = s4_13,
        sex = s1_03,
        age = s1_04,
        relation = s1_08,
        literacy1 = s4_01,
        register1 = s4_05,
        grade = s4_06b,
        repeated = s4_11a,
        income = yhogpc,
        school_level = s4_06a,
        urb_rur = area,
        breakfast = s4_07,
        voucher = s4_08,
        voucher_spent = s4_09,
        educ = e,
        job = cod_16a,
        tasks = s5_16b,
        pov_line = z,
        extr_pov = zext)

hh_2011 <- data_2011 %>% 
  select(hh_id, assist1, reason, sex, age,
         relation, literacy1, register1, school_level, grade, repeated, depto, urb_rur, income, educ, job, tasks, pov_line, extr_pov) %>% 
  mutate(year = 2011,
         dept = case_when(depto == "1" ~ "Chuquisaca",
                          depto == "2" ~ "La Paz",
                          depto == "3" ~ "Cochabamba",
                          depto == "4" ~ "Oruro",
                          depto == "5" ~ "Potosi",
                          depto == "6" ~ "Tarija",
                          depto == "7" ~ "Santa Cruz",
                          depto == "8" ~ "Beni",
                          depto == "9" ~ "Pando"),
           reason = case_when(reason == 1 ~ 'vacation',
                            reason == 2 ~ 'money', 
                            reason == 3 ~ 'work', 
                            reason == 4 ~ 'sickness/accident/disability', 
                            reason == 5 ~ 'distance',
                            reason == 6 ~ 'finished', 
                            reason == 7 ~ 'age',
                            reason == 8 ~ 'not interested', 
                            reason == 9 ~ 'housework/childcare',
                            reason == 10 ~ 'other'),
          literacy = case_when(literacy1 == 1 ~ 1,
                               literacy1 == 2 ~ 0), 
          female = case_when(sex == 2 ~ 1,
                             sex == 1 ~ 0),
           rural = case_when(urb_rur == 1 ~ 0,
                             urb_rur == 2 ~ 1), 
           assist = case_when(assist1 == 1 ~ 1,
                              assist1 == 2 ~ 0),
           register = case_when(register1 == 1 ~ 1,
                                register1 == 2 ~ 0),
         primary = case_when(school_level == 16 ~ 1,
                             school_level != 16 ~ 0),
         secondary = case_when(school_level == 17 ~ 1,
                               school_level != 17 ~ 0))
```

```{r household data 2012}
data_2012 <- read_dta("Raw data/seminar_paper_data/2012_hhsurvey.dta")  %>% 
  rename(hh_id = folio,
        assist1 = s4_12,  
        reason = s4_13,
        sex = s1_03,
        age = s1_04,
        relation = s1_08,
        literacy1 = s4_01,
        register1 = s4_04,
        grade = s4_05b,
        repeated = s4_11a,
        income = yhogpc,
        school_level = s4_05a,
        urb_rur = area,
        depto = departamento,
        breakfast = s4_07,
        voucher = s4_08,
        voucher_spent = s4_09,
        educ = e,
        job = cods5_16a,
        tasks = s5_16b,
        pov_line = z,
        extr_pov = zext)

hh_2012 <- data_2012 %>% 
  select(hh_id, assist1, reason, sex, age,
         relation, literacy1, register1, school_level, grade, repeated, depto, urb_rur, income, educ, job, tasks, pov_line, extr_pov) %>% 
  mutate(year = 2012,
         dept = case_when(depto== "1" ~ "Chuquisaca",
                          depto == "2" ~ "La Paz",
                          depto == "3" ~ "Cochabamba",
                          depto == "4" ~ "Oruro",
                          depto == "5" ~ "Potosi",
                          depto == "6" ~ "Tarija",
                          depto == "7" ~ "Santa Cruz",
                          depto == "8" ~ "Beni",
                          depto == "9" ~ "Pando"),
           reason = case_when(reason == 1 ~ 'vacation',
                            reason == 2 ~ 'money', 
                            reason == 3 ~ 'work', 
                            reason == 4 ~ 'sickness/accident/disability', 
                            reason == 5 ~ 'distance',
                            reason == 6 ~ 'finished', 
                            reason == 7 ~ 'age',
                            reason == 8 ~ 'not interested', 
                            reason == 9 ~ 'housework/childcare',
                            reason == 10 ~ 'other'),
         literacy = case_when(literacy1 == 1 ~ 1,
                              literacy1 == 2 ~ 0), 
         female = case_when(sex == 2 ~ 1,
                            sex == 1 ~ 0),
         rural = case_when(urb_rur == 1 ~ 0,
                           urb_rur == 2 ~ 1), 
         assist = case_when(assist1 == 1 ~ 1,
                            assist1 == 2 ~ 0),
         register = case_when(register1 == 1 ~ 1,
                              register1 == 2 ~ 0),
         primary = case_when(school_level == 19 ~ 1,
                             school_level != 19 ~ 0),
         secondary = case_when(school_level == 20 ~ 1,
                               school_level != 20 ~ 0))

@@

``` {r merging datasets}
total_data<- all_years %>% 
  left_join(flood_summary) %>%
  left_join(drought_summary) %>%
  mutate(child = case_when(relation == 3 ~ 1,
                           relation != 3 ~ 0),
         grandchild = case_when(relation == 8 ~ 1,
                                relation != 8 ~ 0),
         pov_diff = income - pov_line,
         pov = case_when(pov_diff > 0 ~ 0,
                         pov_diff < 0 ~ 1),
         extr_diff = income - extr_pov,
         extr = case_when (extr_diff > 0 ~ 0,
                           extr_diff < 0 ~ 1),
                  work_reason = case_when(reason == "work" ~ 1,
                                 reason != "work" ~ 0),
         money_reason = case_when(reason == "money" ~ 1, 
                                  reason != "money" ~ 0),
         lny = log(income))

total_data %>%
  group_by(work_reason, money_reason) %>%
  summarise(n = n())

@@

hh_head <- subset(total_data, relation == 1, select = c("hh_id", "female", "age", "literacy", "dept", "rural", "income", "year", "educ", "job", "tasks", "pov_diff", "extr_diff", "pov", "extr"))

@@

children <- subset(total_data, age < 18 & age > 4, select = c("hh_id", "age", "female", "child", "grandchild", "literacy", "dept", "rural", "income", "assist", "reason", "register", "primary", "secondary", "floods", "droughts", "year", "job", "tasks", "money_reason", "work_reason"))

@@

total_children %>%
      group_by(child, grandchild) %>%
  summarise(n = n())

total_children %>%
  group_by(work_reason, money_reason) %>%
  summarise(n = n())

@@

```{r combining household head characteristics with children dataset}
hh_head_2 <- hh_head %>%
  select(female, age, literacy, educ, job, tasks, pov, extr, hh_id) %>%
  rename (female_hhhead = female,
          hhhead_age = age,
          hhhead_literacy = literacy,
          hhhead_educ = educ,
          hhhead_job = job,
          hhhead_tasks = tasks)
total_heads_subset <- hh_head_2 %>% distinct()

@@

```{r regression variable specifications}

reg_data <- total_subset %>%
  mutate(year_factor = as.factor(year))

@@

#model_simple <- lm(assist ~ floods + droughts + year, data = reg_data)
#summary(model_simple)
model_assist <- lm(assist ~ floods + droughts + age + female + income + child + grandchild + hhhead_educ + female_hhhead + rural + year_factor, data = reg_data)
summary(model_assist)
#model_register <- lm(register ~ floods + droughts + age + female + income + child + grandchild + hhhead_educ + female_hhhead + rural + year_factor, data = reg_data)
#summary(model_register)

@@

```{r generate regression table, echo = F, results = "asis"}
stargazer::stargazer(list(model_assist_r, model_register_r), 
               title = "Full sample regression results", 
               label = "fullResults",
               header = F,
               keep = c("floods", "droughts"))
```

@@

rural <- subset(reg_data, rural == 1, select = c("hh_id", "id", "age", "female", "literacy", "dept", "rural", "income", "assist", "register", "floods", "droughts", "year", "child", "grandchild", "num_children", "female_hhhead", "hhhead_literacy", "hhhead_educ", "year_factor"))

model_assist_r <- (lm(assist ~ floods + droughts + age + female + income + child + grandchild + num_children + hhhead_educ + female_hhhead + year_factor, data = reg_data))
summary(model_assist_r)
model_register_r <- lm(register ~ floods + droughts + age + female + income + child + grandchild + num_children + hhhead_educ + female_hhhead + year_factor, data = reg_data)
summary(model_register_r)
model_reason <- (lm(work_reason ~ floods + droughts + age + female + income + child + grandchild + num_children + hhhead_educ + female_hhhead + year_factor, data = reg_data))
summary(model_reason)

@@

urban <- subset(reg_data, rural == 0, select = c("hh_id", "id", "age", "female", "literacy", "dept", "rural", "income", "assist", "register", "floods", "droughts", "year", "child", "grandchild", "num_children", "female_hhhead", "hhhead_literacy", "hhhead_educ", "year_factor"))

model_assist_u <- lm(assist ~ floods + droughts + age + female + income + child + grandchild + num_children + hhhead_educ + female_hhhead + year_factor, data = reg_data)
summary(model_assist_u)
model_register_u <- lm(register ~ floods + droughts + age + female + income + child + grandchild + num_children + hhhead_educ + female_hhhead + year_factor, data = reg_data)
summary(model_register_u)
```
